APPM report - Draft

### 2022-12-21 paper_version/main.tex
Finished revision

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{a4paper,scale=0.8}
\usepackage[square,numbers]{natbib}
\bibliographystyle{abbrvnat}
\usepackage{tikz}
\usepackage{tkz-euclide}
\usetikzlibrary{positioning, decorations.markings, arrows, intersections}
\usepackage{nicematrix}
\NiceMatrixOptions{cell-space-top-limit = 4pt}
\NiceMatrixOptions{cell-space-bottom-limit = 4pt}
\usepackage{tcolorbox}
\usepackage{caption, subcaption}
\captionsetup[figure]{labelfont={bf},name={Fig.},labelsep=period}
\captionsetup[table]{labelfont={bf},name={Tab.},labelsep=period}
\setlength\arrayrulewidth{0.7pt}
\usepackage{authblk}
\usepackage{soul}
%\usepackage{showlabels}
\usepackage{multirow}

@@

The material laws (\ref{equ:material_law}) need to be taken into account within this framework, that is, relations $\mathbf{b} = \mathbb{M}_\mu \mathbf{h}$ and $\mathbf{d} = \mathbb{M}_\epsilon \mathbf{e}$ with suitable \emph{material} matrices $\mathbb{M}_\mu, \mathbb{M}_\epsilon$. When the orthogonality of the pair ($\mathcal{M}, \Tilde{\mathcal{M}}$) holds, the discrete material only involve diagonal matrices with entries

\begin{equation*}
    (\mathbb{M}_\mu)_{k,k} = \frac{\mu|A_k|}{|\Tilde{L}_k|}, \ \ \ \ \ (\mathbb{M}_\epsilon)_{k,k} = \frac{\epsilon |\Tilde{A}_k|}{|L_k|},
\end{equation*}
where $|\cdot|$ denotes taking length or area. We would like to remark that the approximation error is introduced due to the implicit assumption that vector fields are piecewise constant, see the analysis in \cite[][Sec. 3.2]{Marrone_2001}.

With the aid of incidence matrices defined in the preceding section and given the discrete material law, (\ref{equ:maxwell_grid_faraday})-(\ref{equ:maxwell_grid_gauss_D}) can be recast into a set of algebraic equations:
\begin{center}
\vspace{-0.5cm}
\begin{minipage}{0.3\textwidth}
\begin{align*}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \\
    \lambda^2\partial_t \mathbf{D} - \nabla \times \mathbf{H} &= -\mathbf{J}, \\
    \nabla \cdot \mathbf{B} &= 0,  \\
    \lambda^2\nabla \cdot \mathbf{D} &= \rho, \\
    \mathbf{H} &= \mu^{-1} \mathbf{B}, \\
    \mathbf{D} &= \epsilon \mathbf{E}. 
\end{align*}
\end{minipage}
\begin{minipage}{0.1\textwidth}
\centering
\begin{tikzpicture}
\draw[thick, -{to}] (0,0) -- node[above]{$(\mathcal{M}, \Tilde{\mathcal{M}})$} (1.5,0);
\end{tikzpicture}
\end{minipage}
\begin{minipage}{0.3\textwidth}
\begin{subequations}
\begin{align}
    \dot{\mathbf{b}} + \mathbb{C}\mathbf{e} &= \mathbf{0} , \label{equ:alg_faraday}\\
    \lambda^2\dot{\mathbf{d}} - \Tilde{\mathbb{C}}\mathbf{h} &= - \mathbf{j}, \label{equ:alg_empere}\\
    \mathbb{D}\mathbf{b} &= \mathbf{0},  \label{equ:alg_gauss_b}\\
    \lambda^2\Tilde{\mathbb{D}}\mathbf{d} &= \mathbf{q},  \label{equ:alg_gauss_d}\\
    \mathbf{h} &= \mathbb{M}_\mu^{-1} \mathbf{b}, \label{equ:alg_material_magnetic}\\
    \mathbf{d} &= \mathbb{M}_{\epsilon} \mathbf{e}, \label{equ:alg_material_electric} 
\end{align}
\end{subequations}
\end{minipage}
\end{center}
where the dot above variables stands for the time derivative.

At this point, we would like to emphasize the importance of the primal-dual staggered meshes: \emph{the material laws can be included in a rather simple way.} For Gauss's law $\mathbf{D} = \epsilon \mathbf{E}$, for instance, the $\mathbf{D}$-field is represented by a collection of face integrals $ \{d_k\}_{k}$ while the $\mathbf{E}$-field is represented by a collection of edge integrals $ \{e_k\}_{k}$. The primal-dual meshes allow us to arrange them in a staggered way -- edges penetrate faces -- such that $\mathbf{D} = \epsilon \mathbf{E}$ can be approximated by $\mathbf{d} = \mathbb{M}_{\epsilon}\mathbf{e}$ in a local fashion, i.e. $\mathbb{M}_{\epsilon}$ is diagonal. A more schematic illustration relies on the language of discrete exterior calculus (DEC), see \cite{bossavit1999, teixeira_1999, hip_1999}.

The essence of FIT lies in: (i) The discrete Maxwell model (\ref{equ:alg_faraday})-(\ref{equ:alg_gauss_d}) are topological in the sense that they are invariant under different coordinate systems. Only the discrete material laws (\ref{equ:alg_material_magnetic})(\ref{equ:alg_material_magnetic}) depend on the geometric information. (ii) The discrete Maxwell model (\ref{equ:alg_faraday})-(\ref{equ:alg_gauss_d}) is free of approximation error, that is, it holds for analytical solutions. The consistency error is only introduced by the discrete material laws (\ref{equ:alg_material_magnetic})(\ref{equ:alg_material_magnetic}).

\subsubsection{Discrete Boundary Conditions}
The electromagnetic boundary $\Gamma_C, \Gamma_I$ is resolved by the primal mesh $\mathcal{M}$. As is mentioned in Section \ref{sec:BC}, the zero magnetic flux $\mathbf{B}\cdot \mathbf{n}$ is equivalent to $\nabla\times\mathbf{E} \cdot \mathbf{n} = 0$, which allows a boundary scalar potential $\varphi$ such that the tangential component $\mathbf{E}_t$ of the $\mathbf{E}$-field is equal to $\nabla_\Gamma\varphi$. It holds on the discrete level as well. We associate each primal vertex $P_k \in \partial\Omega$ with a scalar value $\varphi_k$. Therefore, the boundary conditions (see Section \ref{sec:BC}) are discretized in the following way:
\begin{center}
    \vspace{-0.5cm}
    \begin{minipage}{0.3\textwidth}
    \begin{align*}
    \mathbf{D} \cdot \mathbf{n} = 0\ \ &\text{on} \ \  \Gamma_I,  \\
    \mathbf{B} \cdot \mathbf{n} = 0\ \  &\text{on} \ \  \Gamma_I, \\
    \varphi = \varphi^\pm(t)\ \ &\text{on} \ \ \Gamma_C^\pm,
    \end{align*}
    \end{minipage}
    \begin{minipage}{0.1\textwidth}
    \centering
    \begin{tikzpicture}
    \draw[thick, -{to}] (0,0) -- node[above]{$(\mathcal{M}, \Tilde{\mathcal{M}})$} (1.5,0);
    \end{tikzpicture}
    \end{minipage}
    \begin{minipage}{0.5\textwidth}
        \centering
        \begin{subequations}
            \begin{align}
            d_k = 0,\ \ &\forall k : \Tilde{A}_k \subset \Gamma_I,\label{equ:bc_3} \\
            e_k = (\mathbb{GX}_\varphi\bm{\varphi})_k,\ \ &\forall k : L_k \subset \partial\Omega, \label{equ:bc_2}\\
            \varphi_k = \varphi^\pm(t), \ \ &\forall k : P_k \subset \Gamma_C^\pm, \label{equ:bc_1}
            \end{align}
        \end{subequations}
    \end{minipage}
\end{center}
where $\mathbb{X}_\varphi \in \mathbb{R}^{N_P \times N_P^\partial}$ extends $\bm{\varphi}$ to all the primal verices by zero. Therefore, the surface gradient $\nabla_\Gamma$ is represented by $\mathbb{GX}_\varphi$.

\subsubsection{Stabilization in $\Omega_N$} \label{sec:reform-discrete}
In Section \ref{sec:reform_continuous}, we have proposed a stabilization of the Maxwell system in the non-conducting domain $\Omega_N$ by introducing a Lagrange multiplier. In the semi-discrete level, the equations to be solved in $\Omega_N$ are

\begin{center}
    \vspace{-0.5cm}
    \begin{minipage}{0.3\textwidth}
    \begin{align*}
        \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \\ 
        \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} + \colorbox{orange!20}{$\nabla \psi$} &= 0, \\
        \nabla \cdot \mathbf{D} &= 0. 
    \end{align*}
    \end{minipage}
    \begin{minipage}{0.1\textwidth}
    \centering
    \begin{tikzpicture}
    \draw[thick, -{to}] (0,0) -- node[above]{$(\mathcal{M}, \Tilde{\mathcal{M}})$} (1.5,0);
    \end{tikzpicture}
    \end{minipage}
    \begin{minipage}{0.5\textwidth}
        \begin{subequations}
        \begin{align}
            [\dot{\mathbf{b}} + \mathbb{C}\mathbf{e} &= \mathbf{0}]_k,\ \ \forall k:A_k \subset \Omega_N,\\
            [\lambda^2\dot{\mathbf{d}} - \Tilde{\mathbb{C}}\mathbf{h} + \colorbox{orange!20}{$\mathbb{H} \mathbb{G} \mathbb{X}_\psi \bm{\psi}$}&= \mathbf{0}]_k, \ \ \forall k: \Tilde{A}_k \subset \Omega_N \label{equ:discrete_ampere_ins}\\
            [\Tilde{\mathbb{D}}\mathbf{d} &= \mathbf{0}]_k,\ \ \forall k:\Tilde{V}_k \subset \Omega_N \label{equ:discrete_zero_div}, 
        \end{align} 
    \end{subequations}
    \end{minipage}
\end{center}
where $\bm{\psi} := \{\psi_k\}_{k=1}^{N_P^N}$ denotes unknowns assigned to each primal vertex in $\Omega_N$. The matrix $\mathbb{X}_\psi \in \mathbb{R}^{N_P \times N_P^{N}}$ extends $\bm{\psi}$ by zero to all the primal vertices, by which the zero Dirichlet boundary condition is incorporated. We need the matrix $(\mathbb{H})_{k,k} = {|\Tilde{A}_k|}/{|L_k|}$ to transform primal edge integrals to dual face fluxes since the discrete Amp\`{e}re's law (\ref{equ:discrete_ampere_ins}) is defined on dual faces on $\Omega_N$.

@@

We can examine the well-posedness of the (semi-)discrete Maxwell system by checking whether the numbers of unknowns (also called degrees of freedom (D.o.F.)) and equations coincide.

First, we make a meticulous classification for mesh entities according to their locations:
\begin{center}
\vspace{-0.5cm}
\begin{minipage}[t]{0.4\textwidth}
    \begin{align*}
        &\#\  \text{primal cells}\ \  N_V \\
        &\#\  \text{primal edges}\ \  N_L := \underbrace{N^C_L + N^I_L}_{=N^\partial_L} + N^\circ_L  \\
        &\#\  \text{primal faces}\ \  N_A := \underbrace{N_A^C + N^I_A}_{=N^\partial_A} + N^\circ_A  \\
        &\#\  \text{primal vertices}\ \  N_P := \underbrace{N_P^C + N^I_P}_{=N^\partial_P} + N^\circ_P
    \end{align*}
\end{minipage}
\begin{minipage}[t]{0.4\textwidth}
    \begin{align*}
        &\#\  \text{dual cells}\ \  N_{\Tilde{V}} := N_P \\
        &\#\  \text{dual edges}\ \  N_{\Tilde{L}} := \underbrace{N^\partial_{\Tilde{L}}}_{=N^\partial_L} + \underbrace{N^\circ_{\Tilde{L}}}_{=N_A} \\
        &\#\  \text{dual faces}\ \  N_{\Tilde{A}} := \underbrace{N^\partial_{\Tilde{A}}}_{=N^\partial_P} + \underbrace{N^\circ_{\Tilde{A}}}_{=N_L}
    \end{align*}
\end{minipage}   
\end{center}
where the superscript indicates the locations where the entities lie. The equations $N^\partial_{\Tilde{L}} = N^\partial_L, N^\partial_{\Tilde{A}} = N^\partial_P$ reveal the bijective relation between the boundary primal entities and auxiliary entities, as can be checked easily by inspecting Fig. \ref{fig:illustraion_dual_boundary}.
We also give a summary of the unknowns in Tab. \ref{tab:def_size_var}.
\begin{table}[]
    \centering
\begin{tabular}{c c c}
     \hline
     Vector of unknowns  & Meaning  & Vector size \\
     \hline
     $\mathbf{e}$ & line integrals of $\mathbf{E}$-field at primal edges $L$& $N_L$ \\
     $\bm{\varphi}$ & boundary scalar potential $\varphi$ at primal vertices $P$ on $\partial\Omega$ & $N_P^\partial$ \\
     $\mathbf{b}$ & surface integrals of $\mathbf{B}$-field at primal faces $A$ & $N_A$ \\
     $\mathbf{h}$ & line integrals of $\mathbf{H}$-field at dual edges $\Tilde{L}$ & $N_{\Tilde{L}}$ \\
     $\mathbf{d}$ & surface integrals of $\mathbf{D}$-field at dual faces $\Tilde{A}$ & $N_{\Tilde{A}}$ \\
     $\bm{\psi}$ & Lagrange multiplier $\psi$ at primal vertices $P$ in $\Omega_N$ & $N^{N}_P$\\ 
     \hline
\end{tabular}
    \caption{Definitions and sizes of the vectors of unknowns.}
    \label{tab:def_size_var}
\end{table}

Next, we collect all the algebraic equations derived from the Maxwell system and the boundary conditions: 
\begin{align*}
    \text{discrete Faraday's law (\ref{equ:alg_faraday})} \ \ &\longrightarrow\ \  N_A \ \ \text{equations} \\
    \text{discrete Ampere's law (\ref{equ:alg_empere})} \ \ &\longrightarrow\ \  N_{\Tilde{A}} \ \ \text{equations} \\
    \text{discrete material laws (\ref{equ:alg_material_magnetic})(\ref{equ:alg_material_electric})} \ \ &\longrightarrow\ \  N_A + N_L \ \ \text{equations} \\
    \text{boundary condition (\ref{equ:bc_1})} \ \ &\longrightarrow\ \  N_P^C \ \ \text{equations} \\
    \text{boundary condition (\ref{equ:bc_2})} \ \ &\longrightarrow\ \  N_L^\partial \ \ \text{equations} \\
    \text{boundary condition (\ref{equ:bc_3})} \ \ &\longrightarrow\ \  N_{\Tilde{A}}^I \ \ \text{equations}. \\
    \text{vanishing divergence constraint (\ref{equ:discrete_zero_div})} \ \ &\longrightarrow\ \  N_{\Tilde{V}}^{N} \ \ \text{equations}. \\
\end{align*}
Comparing the numbers of D.o.F in Tab. \ref{tab:def_size_var} and of the equations we collect above, we show that they are equal:
\begin{align*}
    \#\text{ of unknowns} &= \colorbox{violet!20}{$N_L$} + \colorbox{blue!20}{$N_A$} + \colorbox{gray!40}{$N_{\Tilde{L}}$} + \colorbox{orange!20}{$N_{\Tilde{A}}$} + \colorbox{green!20}{$N_P^\partial$} + \colorbox{yellow!40}{$N_P^{N}$}, \\
    \#\text{ of equations} &= \colorbox{blue!20}{$N_A$} + \colorbox{orange!20}{$N_{\Tilde{A}}$} + \colorbox{gray!40}{$N_A+N_L^\partial$} + \colorbox{violet!20}{$N_L$} + \colorbox{green!20}{$N_P^C + N_P^I$}+ \colorbox{yellow!40}{$N_{\Tilde{V}}^N$},
\end{align*}
where the terms with the same color are equal.

Of course, the matching numbers of unknowns and equations do not necessarily result in a valid linear system, since the equations might be linearly dependent. In fact, the linear system will be singular without the stabilization proposed in the previous section when $\lambda = 0$.

\subsection{Discrete Euler Equations} \label{sec:discrete_euler}
We employ the finite volume method (FVM) to discretize the Euler system. The Euler equations (\ref{equ:euler_}) can be cast into the form of conservation law with source terms:
\begin{equation} \label{equ:euler_conservation}
    \partial_t \mathbf{U} + \nabla \cdot \mathbf{f}(\mathbf{U}) = \mathbf{RHS},
\end{equation}
where $\mathbf{U} \in L^2(\Omega \times [0,T], \mathbb{R}^m)$ stands for $m$ conservative variables. In the case of the full 3D Euler equations (\ref{equ:euler_rescaled}), $m = 5$ and $\mathbf{U} := [n, n\mathbf{u}, ne]$. $\mathbf{f}(\mathbf{U}) \in L^2(\Omega \times  [0,T], \mathbb{R}^{3 \times m})$ is the flux function. $\mathbf{RHS} \in L^2(\Omega \times  [0,T], \mathbb{R}^m)$ is the source term.

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{a4paper,scale=0.8}
\usepackage[square,numbers]{natbib}
\bibliographystyle{abbrvnat}
\usepackage{tikz}
\usepackage{tkz-euclide}
\usetikzlibrary{positioning, decorations.markings, arrows, intersections}
\usepackage{nicematrix}
\NiceMatrixOptions{cell-space-top-limit = 4pt}
\NiceMatrixOptions{cell-space-bottom-limit = 4pt}
\usepackage{tcolorbox}
\usepackage{caption, subcaption}
\captionsetup[figure]{labelfont={bf},name={Fig.},labelsep=period}
\captionsetup[table]{labelfont={bf},name={Tab.},labelsep=period}
\setlength\arrayrulewidth{0.7pt}
\usepackage{authblk}
\usepackage{soul}
%\usepackage{showlabels}
\usepackage{multirow}

@@

The material laws (\ref{equ:material_law}) need to be taken into account within this
framework, that is, relations $\mathbf{b} = \mathbb{M}_\mu \mathbf{h}$ and $\mathbf{d} =
\mathbb{M}_\epsilon \mathbf{e}$ with suitable \emph{material} matrices $\mathbb{M}_\mu,
\mathbb{M}_\epsilon$. When the orthogonality of the pair ($\mathcal{M},
\Tilde{\mathcal{M}}$) holds, the discrete material laws can consistently be represented by
\emph{diagonal matrices} with entries
\begin{equation*}
    (\mathbb{M}_\mu)_{k,k} = \frac{\mu|A_k|}{|\Tilde{L}_k|}, \ \ \ \ \ (\mathbb{M}_\epsilon)_{k,k} = \frac{\epsilon |\Tilde{A}_k|}{|L_k|},
\end{equation*}
where $|\cdot|$ denotes taking length or area. We would like to remark that an
approximation error is introduced due to the implicit assumption that vector fields are
piecewise constant, see the analysis in \cite[][Sec. 3.2]{Marrone_2001}.

With the aid of incidence matrices defined in the preceding section and given the discrete
material law, (\ref{equ:maxwell_grid_faraday})-(\ref{equ:maxwell_grid_gauss_D}) can be
recast into a set of algebraic equations:
\begin{center}
\vspace{-0.5cm}
\begin{minipage}{0.3\textwidth}
\begin{align*}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \\
    \lambda^2\partial_t \mathbf{D} - \nabla \times \mathbf{H} &= -\mathbf{J}, \\
    \nabla \cdot \mathbf{B} &= 0,  \\
    \lambda^2\nabla \cdot \mathbf{D} &= \rho, \\
    \mathbf{H} &= \mu^{-1} \mathbf{B}, \\
    \mathbf{D} &= \epsilon \mathbf{E}. 
\end{align*}
\end{minipage}
\begin{minipage}{0.1\textwidth}
\centering
\begin{tikzpicture}
\draw[thick, -{to}] (0,0) -- node[above]{$(\mathcal{M}, \Tilde{\mathcal{M}})$} (1.5,0);
\end{tikzpicture}
\end{minipage}
\begin{minipage}{0.3\textwidth}
\begin{subequations}
\begin{align}
    \dot{\mathbf{b}} + \mathbb{C}\mathbf{e} &= \mathbf{0} , \label{equ:alg_faraday}\\
    \lambda^2\dot{\mathbf{d}} - \Tilde{\mathbb{C}}\mathbf{h} &= - \mathbf{j}, \label{equ:alg_empere}\\
    \mathbb{D}\mathbf{b} &= \mathbf{0},  \label{equ:alg_gauss_b}\\
    \lambda^2\Tilde{\mathbb{D}}\mathbf{d} &= \mathbf{q},  \label{equ:alg_gauss_d}\\
    \mathbf{h} &= \mathbb{M}_\mu^{-1} \mathbf{b}, \label{equ:alg_material_magnetic}\\
    \mathbf{d} &= \mathbb{M}_{\epsilon} \mathbf{e}, \label{equ:alg_material_electric} 
\end{align}
\end{subequations}
\end{minipage}
\end{center}
where the dot on top of quantities stands for the time derivative.

\begin{remark}
  At this point, we would like to emphasize the importance of the primal-dual staggered
  meshes: \emph{the material laws can be included in a rather simple way.} For Gauss's law
  $\mathbf{D} = \epsilon \mathbf{E}$, for instance, the $\mathbf{D}$-field is represented
  by a collection of face integrals $ \{d_k\}_{k}$ while the $\mathbf{E}$-field is
  represented by a collection of edge integrals $ \{e_k\}_{k}$. The primal-dual meshes
  allow us to arrange them in a staggered way -- edges penetrate faces -- such that
  $\mathbf{D} = \epsilon \mathbf{E}$ can be approximated by
  $\mathbf{d} = \mathbb{M}_{\epsilon}\mathbf{e}$ in a local fashion,
  i.e. $\mathbb{M}_{\epsilon}$ is diagonal. A more schematic illustration relies on the
  language of discrete exterior calculus (DEC), see \cite{bossavit1999, teixeira_1999,
    hip_1999}.
\end{remark}

Summing up, the essence of DEC/FIT is the following:
\begin{enumerate}[label={(\roman{*})}]
\item The discrete Maxwell model (\ref{equ:alg_faraday})-(\ref{equ:alg_gauss_d}) are
  topological in the sense that they are invariant under different coordinate
  systems. Only the discrete material laws
  (\ref{equ:alg_material_magnetic})(\ref{equ:alg_material_magnetic}) depend on the
  geometric information.
\item The discrete Maxwell model (\ref{equ:alg_faraday})-(\ref{equ:alg_gauss_d}) is free
  of approximation error, that is, it holds for exact fields. A consistency error is
  introduced only by the discrete material laws
  (\ref{equ:alg_material_magnetic})(\ref{equ:alg_material_magnetic}).
\end{enumerate}

\subsubsection{Discrete Boundary Conditions}

The electromagnetic boundary $\partial\Omega = \Gamma_C\cup \Gamma_I$ is resolved by the
primal mesh $\mathcal{M}$. As is mentioned in Section \ref{sec:BC}, the zero-magnetic-flux
boundary condition $\mathbf{B}\cdot \mathbf{n}$ is equivalent to
$(\nabla\times\mathbf{E}) \cdot \mathbf{n} = 0$, which paves the way for a surface scalar
potential $\varphi:\partial\Omega\to\mathbb{R}$ such that the tangential component
$\mathbf{E}_t$ of the $\mathbf{E}$-field is equal to $\nabla_\Gamma\varphi$. This remains
true on the discrete level. We associate with each primal vertex $P_k \in \partial\Omega$
a scalar value $\varphi_k$. Therefore, the boundary conditions (see Section \ref{sec:BC})
are discretized in the following way:
\begin{center}
    \vspace{-0.5cm}
    \begin{minipage}{0.3\textwidth}
    \begin{align*}
    \mathbf{D} \cdot \mathbf{n} = 0\ \ &\text{on} \ \  \Gamma_I,  \\
    \mathbf{B} \cdot \mathbf{n} = 0\ \  &\text{on} \ \  \Gamma_I, \\
    \varphi = \varphi^\pm(t)\ \ &\text{on} \ \ \Gamma_C^\pm,
    \end{align*}
    \end{minipage}
    \begin{minipage}{0.1\textwidth}
    \centering
    \begin{tikzpicture}
    \draw[thick, -{to}] (0,0) -- node[above]{$(\mathcal{M}, \Tilde{\mathcal{M}})$} (1.5,0);
    \end{tikzpicture}
    \end{minipage}
    \begin{minipage}{0.5\textwidth}
        \centering
        \begin{subequations}
            \begin{align}
            d_k = 0,\ \ &\forall k : \Tilde{A}_k \subset \Gamma_I,\label{equ:bc_3} \\
            e_k = (\mathbb{GX}_\varphi\bm{\varphi})_k,\ \ &\forall k : L_k \subset \partial\Omega, \label{equ:bc_2}\\
            \varphi_k = \varphi^\pm(t), \ \ &\forall k : P_k \subset \Gamma_C^\pm, \label{equ:bc_1}
            \end{align}
        \end{subequations}
    \end{minipage}
\end{center}
where $\mathbb{X}_\varphi \in \mathbb{R}^{N_P \times N_P^\partial}$ extends $\bm{\varphi}$
to all the primal verices by zero. Obviously, the surface gradient $\nabla_\Gamma$ is
represented by $\mathbb{GX}_\varphi$.

\subsubsection{Stabilization in $\Omega_N$} \label{sec:reform-discrete}

In Section \ref{sec:reform_continuous}, we have proposed a stabilization of the Maxwell
system in the non-conducting domain $\Omega_N$ by introducing a Lagrange multiplier. On
the semi-discrete level, the equations to be solved in $\Omega_N$ are
\begin{center}
    \begin{minipage}{0.3\textwidth}
    \begin{align*}
        \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \\ 
        \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} + \colorbox{orange!20}{$\nabla \psi$} &= 0, \\
        \nabla \cdot \mathbf{D} &= 0. 
    \end{align*}
    \end{minipage}
    \begin{minipage}{0.1\textwidth}
    \centering
    \begin{tikzpicture}
    \draw[thick, -{to}] (0,0) -- node[above]{$(\mathcal{M}, \Tilde{\mathcal{M}})$} (1.5,0);
    \end{tikzpicture}
    \end{minipage}
    \begin{minipage}{0.5\textwidth}
        \begin{subequations}
        \begin{align}
            [\dot{\mathbf{b}} + \mathbb{C}\mathbf{e} &= \mathbf{0}]_k,\ \ \forall k:A_k \subset \Omega_N,\\
            [\lambda^2\dot{\mathbf{d}} - \Tilde{\mathbb{C}}\mathbf{h} + \colorbox{orange!20}{$\mathbb{H} \mathbb{G} \mathbb{X}_\psi \bm{\psi}$}&= \mathbf{0}]_k, \ \ \forall k: \Tilde{A}_k \subset \Omega_N \label{equ:discrete_ampere_ins}\\
            [\Tilde{\mathbb{D}}\mathbf{d} &= \mathbf{0}]_k,\ \ \forall k:\Tilde{V}_k \subset \Omega_N \label{equ:discrete_zero_div}, 
        \end{align} 
    \end{subequations}
    \end{minipage}
\end{center}
where $\bm{\psi} := \{\psi_k\}_{k=1}^{N_P^N}$ denotes unknowns assigned to each primal
vertex in $\Omega_N$. The matrix $\mathbb{X}_\psi \in \mathbb{R}^{N_P \times N_P^{N}}$
extends $\bm{\psi}$ by zero to all the primal vertices. This way the zero Dirichlet
boundary condition is incorporated. We need the diagonal matrix
$(\mathbb{H})_{k,k} = {|\Tilde{A}_k|}/{|L_k|}$ to transform primal edge integrals to dual
face fluxes since the discrete Amp\`{e}re's law (\ref{equ:discrete_ampere_ins}) is defined
on dual faces on $\Omega_N$.

@@

We can probe the well-posedness of the (semi-)discrete Maxwell system by checking whether
the numbers of unknowns (also called degrees of freedom (D.o.F.)) and equations coincide.
First, we count mesh entities according to their locations:
\begin{center}
\vspace{-0.5cm}
\begin{minipage}[t]{0.4\textwidth}
    \begin{align*}
        &\#\  \text{primal cells}\ \  N_V, \\
        &\#\  \text{primal edges}\ \  N_L := \underbrace{N^C_L + N^I_L}_{=N^\partial_L} + N^\circ_L,  \\
        &\#\  \text{primal faces}\ \  N_A := \underbrace{N_A^C + N^I_A}_{=N^\partial_A} + N^\circ_A , \\
        &\#\  \text{primal vertices}\ \  N_P := \underbrace{N_P^C + N^I_P}_{=N^\partial_P} + N^\circ_P,
    \end{align*}
\end{minipage}
\begin{minipage}[t]{0.4\textwidth}
    \begin{align*}
        &\#\  \text{dual cells}\ \  N_{\Tilde{V}} := N_P ,\\
        &\#\  \text{dual edges}\ \  N_{\Tilde{L}} := \underbrace{N^\partial_{\Tilde{L}}}_{=N^\partial_L} + \underbrace{N^\circ_{\Tilde{L}}}_{=N_A} ,\\
        &\#\  \text{dual faces}\ \  N_{\Tilde{A}} := \underbrace{N^\partial_{\Tilde{A}}}_{=N^\partial_P} + \underbrace{N^\circ_{\Tilde{A}}}_{=N_L},
    \end{align*}
\end{minipage}   
\end{center}
where the superscripts indicate where the entities are located. The equalities
$N^\partial_{\Tilde{L}} = N^\partial_L, N^\partial_{\Tilde{A}} = N^\partial_P$ reveal the
bijective relation between the boundary primal entities and auxiliary entities, as can be
checked easily by inspecting Fig.~\ref{fig:illustraion_dual_boundary}.  We also give a
summary of the unknowns in Tab.~\ref{tab:def_size_var}.
\begin{table}[]
    \centering
\begin{tabular}{c c c}
     \hline
     Vector of unknowns  & Meaning  & Vector size \\
     \hline
     $\mathbf{e}$ & line integrals of $\mathbf{E}$-field at primal edges $L$& $N_L$ \\
     $\bm{\varphi}$ & boundary scalar potential $\varphi$ at primal vertices $P$ on $\partial\Omega$ & $N_P^\partial$ \\
     $\mathbf{b}$ & surface integrals of $\mathbf{B}$-field at primal faces $A$ & $N_A$ \\
     $\mathbf{h}$ & line integrals of $\mathbf{H}$-field at dual edges $\Tilde{L}$ & $N_{\Tilde{L}}$ \\
     $\mathbf{d}$ & surface integrals of $\mathbf{D}$-field at dual faces $\Tilde{A}$ & $N_{\Tilde{A}}$ \\
     $\bm{\psi}$ & Lagrange multiplier $\psi$ at primal vertices $P$ in $\Omega_N$ & $N^{N}_P$\\ 
     \hline
\end{tabular}
    \caption{Definitions and sizes of the vectors of unknowns.}
    \label{tab:def_size_var}
\end{table}

Next, we collect all the algebraic equations derived from the Maxwell system and the boundary conditions: 
\begin{align*}
    \text{discrete Faraday's law (\ref{equ:alg_faraday})} \ \ &\longrightarrow\ \  N_A \ \ \text{equations} \\
    \text{discrete Ampere's law (\ref{equ:alg_empere})} \ \ &\longrightarrow\ \  N_{\Tilde{A}} \ \ \text{equations} \\
    \text{discrete material laws (\ref{equ:alg_material_magnetic})(\ref{equ:alg_material_electric})} \ \ &\longrightarrow\ \  N_A + N_L \ \ \text{equations} \\
    \text{boundary condition (\ref{equ:bc_1})} \ \ &\longrightarrow\ \  N_P^C \ \ \text{equations} \\
    \text{boundary condition (\ref{equ:bc_2})} \ \ &\longrightarrow\ \  N_L^\partial \ \ \text{equations} \\
    \text{boundary condition (\ref{equ:bc_3})} \ \ &\longrightarrow\ \  N_{\Tilde{A}}^I \ \ \text{equations}. \\
    \text{vanishing divergence constraint (\ref{equ:discrete_zero_div})} \ \ &\longrightarrow\ \  N_{\Tilde{V}}^{N} \ \ \text{equations}. \\
\end{align*}
Comparing the numbers of d.o.f. in Tab.~\ref{tab:def_size_var} and of the equations we
collect above, we see that they are equal:
\begin{align*}
    \#\text{ of unknowns} &= \colorbox{violet!20}{$N_L$} + \colorbox{blue!20}{$N_A$} + \colorbox{gray!40}{$N_{\Tilde{L}}$} + \colorbox{orange!20}{$N_{\Tilde{A}}$} + \colorbox{green!20}{$N_P^\partial$} + \colorbox{yellow!40}{$N_P^{N}$}, \\
    \#\text{ of equations} &= \colorbox{blue!20}{$N_A$} + \colorbox{orange!20}{$N_{\Tilde{A}}$} + \colorbox{gray!40}{$N_A+N_L^\partial$} + \colorbox{violet!20}{$N_L$} + \colorbox{green!20}{$N_P^C + N_P^I$}+ \colorbox{yellow!40}{$N_{\Tilde{V}}^N$}.
\end{align*}
Of course, the matching numbers of unknowns and equations do not necessarily result in a
valid linear system, since the equations might be linearly dependent. In fact, the linear
system will be singular without the stabilization proposed in the previous section when
$\lambda = 0$.

\subsection{Discrete Euler Equations} \label{sec:discrete_euler}

We employ the finite volume method (FVM) to discretize the Euler system. The Euler
equations (\ref{equ:euler_}) can be cast into the form of conservation law with source
terms:
\begin{equation} \label{equ:euler_conservation}
    \partial_t \mathbf{U} + \nabla \cdot \mathbf{f}(\mathbf{U}) = \mathbf{RHS},
\end{equation}
where $\mathbf{U} \in L^2(\Omega \times [0,T], \mathbb{R}^m)$ stands for a vector of $m$
conservative variables,
$\mathbf{f}(\mathbf{U}) \in L^2(\Omega \times [0,T], \mathbb{R}^{3 \times m})$ is the flux
function, and $\mathbf{RHS} \in L^2(\Omega \times [0,T], \mathbb{R}^m)$ is the source
term.. In the case of the full 3D Euler equations (\ref{equ:euler_rescaled}), $m = 5$ and
$\mathbf{U} := [n, n\mathbf{u}, ne]$.
